Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-03 mu/article/article.tex
Alt redaction at half completion.

\documentclass[]{article}
% \documentclass[twocolumn]{article}

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[inline  ]{showlabels}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/altstruc1}\hspace{0.05\textwidth}
    \includegraphics[width=0.45\textwidth]{figures/altstruc2}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/upstruc1}\hspace{0.05\textwidth}
    \includegraphics[width=0.45\textwidth]{figures/upstruc2}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-1}\hspace{0.05\textwidth}
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-1}\hspace{0.05\textwidth}
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% % section introuction (end)

\section{Theory} % (fold)
\label{sec:theory}
The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
plane is given by
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)E^{2}(\omega)\cos^{2}\theta + 
\mu^{\mathrm{abyy}}(\omega)E^{2}(\omega)\sin^{2}\theta + 
2\mu^{\mathrm{abxy}}(\omega)E^{2}(\omega)\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}(\omega)E^{2}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)E^{2}(\omega)\sin^{2}\theta},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}\theta + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}\theta + 2\mu^{\mathrm{abxy}}(\omega)\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)\sin^{2}\theta}.
\label{eq:vab}
\end{align}
For an angle $\theta = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

@@

@@

\begin{table}[tb]
\caption{Unit cell of \emph{alt} structure.}
\center
\begin{tabular}{ccccc}\label{tab:altunitcell}  \\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline\\
\end{tabular} \\
\begin{minipage}{0.42\textwidth}
Layer division, atom types and positions for the \emph{alt} structure.
The structure unit cell was divided in six layers corresponding each one to
atoms in different $z$ positions.
\end{minipage}
\end{table}

\begin{table}[tb]
\caption{Unit cell of \emph{up} structure.}
\center
\begin{tabular}{ccccc}\label{tab:upunitcell}  \\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline\\
\end{tabular} \\
\begin{minipage}{0.42\textwidth}
Layer division, atom types and positions for the \emph{up} structure.
The structure unit cell was divided in two layers corresponding to
hydrogen and carbon atoms.
\end{minipage}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{alt} % (fold)
\label{sec:results-alt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{xb}}$}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components.}
    \label{fig:alt-xbangcomp}
\end{figure}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{yb}}$}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:alt-rtp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vyz-layers.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:alt-lay}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-comp.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:alt-comp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{yb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yz-angcomp.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:up-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vyb1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 1.8--2.1 eV }

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magxbincang2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magybincang2}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb2}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-1.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-1.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-1.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-1.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-2.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-2.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-2.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-2.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

>>>>

% \documentclass[]{article}
\documentclass[twocolumn]{article}

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cuted}
\usepackage{blindtext}
\usepackage{color}
\usepackage[inline]{showlabels}
\usepackage{showframe}

@@

\textcolor{red}{
{\huge Filling with text.}\\
\blindtext
}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% % section introuction (end)
\textcolor{red}{
\blindtext
\blindtext
\blindtext
}

\section{Theory} % (fold)
\label{sec:theory}
The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
plane with a polarization angle $\alpha$ is given by

\begin{strip}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{strip}

For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions.}
\label{tab:altunitcell}
\end{table}

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.}
\label{tab:upunitcell}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}

In Fig. \ref{fig:alt-magvxbincang} we present the $\mathcal{V}^{\mathrm{x}}$
spectra resulting from evaluate the Eq. \eqref{eq:vab-mag} at using different
polarization angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_16$H$_8$-alt
structure. The onset of the response is when the energy of the incoming light is
the same of the gap energy. From this picture we can see that for the zone
between the energy range of 0.90\,eV-0.93\,eV and polarization angles between
120$^{\circ}$ and 150$^{\circ}$ is the zone of the maximum response is held
reaching values of $\mathcal{V}^{\mathrm{x}}$ near to 30\,Km/s. Also there is a
second zone between the energy range of 0.70\,eV-0.74\,eV and same polarization
angles where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near
to 22\,Km/s.We also found that the absolute maximum of the response is obtained
for a polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
contribute with almost the same intensity. In the other hand, for the energy
range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
$\mathcal{V}^{\mathrm{xz}}$ component.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{$\mathcal{V}^{\mathrm{x}}$ for C$_16$H$_8$-alt structure. The
    maximum response zone is localized for an energy range from 0.90\,eV to
    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}

\begin{figure}[]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{y}}$}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:alt-rtp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:alt-lay}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:alt-comp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
    \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:up-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
    \label{fig:up-vyb1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

@@

\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magxbincang2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magybincang2}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb2}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}
